The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-12-03 manuscript/manuscript.qmd
Update legal and DV section

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.

@@

As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs. TODO describe the province count variable

@@

# Contentiousness and government relationships: The cases of Greenpeace and The Nature Conservancy

>>>>

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find suitable PSUs can end up not being able to registered or registered with great limitation in terms of work areas and geographical reach. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province.

@@

As explained, the dependent variable is the count of provinces that INGOs are authorized to work in as documented in their official registration record. The documentation lists the specific provincial regions each INGO RO can conduct activities in and we derive the number of provinces based on the lists. Since the maximum count of provinces INGOs can possibly work in is 32, this variable ranges from 1 to 32.

@@

# Contentiousness and government relationships: The cases ofThe Nature Conservancy and Greenpeace
